A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-01 mt-marathon.2013/PBML_article.tex
start adding bibs

This paper describes this new feature function framework as implemented in the Moses decoder, a compares it with that implemented in cdec\cite{Dyer_etal_2010} and Joshua\cite{Joshua-Decoder}.

>>>>

This paper describes this new feature function framework as implemented in the Moses decoder, and compares it with that implemented in cdec\cite{Dyer_etal_2010} and Joshua\cite{Joshua-Decoder}.
